Commutative Character Sheaves on smooth group schemes over finite fields

### 2016-02-23 followup.tex
Adding reference to bibliography
Yay Loren!

For use below, we recall some basic facts about the Heisenberg-Weil representation and make a conjecture about the geometrization of these representations.
We refer the reader to \cite{BS} for more detail.

@@

As proved in \cite{kim:07a}, all supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}.
The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from Yu's data. 
Let us refer to the types arising in this manner as {\it Yu types}.
%In this section we show that every Yu type is geometrizable.
% in a sense which will be made clear below.
%
A Yu type is then a pair $(C,\rho)$, where $C$ is a compact group and $\rho$ is a representation of $C$, directly from the following information, derived from a Yu datum:
\begin{enumerate}
\labitem{Y0}{Y0} a sequence of compact groups $C^0 \subseteq C^1 \subseteq \cdots \subseteq C^d= C$;
\labitem{Y1}{Y1} a continuous representation $\rho^0$ of $C^0$;
\labitem{Y2}{Y2} a quasicharacter $\varphi^i : C^i \to \CC^\times$, for $i=0, \ldots d$.
\end{enumerate}
The representations $(\rho^0, \varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct representations $\rho^i$ of $C^i$, for $i=1, \ldots, d$ such that $\rho^d = \rho$.

Since we will need some facts about this construction, we review some further detail here.
First, Yu introduces 
\begin{enumerate}
\labitem{Y3}{Y3}
compact groups $J^i\subset C$, for $i=0, \ldots d$, such that 
$
C^i = J^0\cdots J^{i}
$ 
and, for $i=0, \ldots d-1$, a natural action of $C^i$ on $J^{i+1}$ defining the groups $C^i \ltimes J^{i+1}$.
\begin{equation}\label{eq:semiprod}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && C^{i}\cap J^{i+1}\arrow{d} && \\
1 \arrow{r} & J^{i+1} \arrow{r} & C^i \ltimes J^{i+1} \arrow{d}{\pi_{i+1}} \arrow{r}{p_i} & C^i \arrow{r} & 1\\
&& C^{i+1} \arrow{d}{} && \\
&& 1 &&
\end{tikzcd}
\end{equation}
\end{enumerate}
%He then introduces the following quotients of $J^{i+1}$ and $C^i$, for $i=0, \ldots d-1$.
Next, Yu uses this to define a group homomorphism (in fact, a quotient) 
$
J^{i+1} \to V_{i+1}
$
where $V_{i+1}$ is a finite abelian group, the latter also given the structure of a $\Fq$-vector space.
The vector space $V_{i+1}$ is then equipped with a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$, where $C_{i+1}$ is a one-dimensional vector space over $\Fq$, itself equipped with an additive character $\psi_{i+1} : C_{i+1} \to \EEx$.
%\labitem{Q2}{Q2} 
%\item 
This, in turn, is used to define a map
$
J^{i+1} \to V_{i+1}^\sharp,
$
where $V_{i+1}^\sharp$ is the Heisenberg group determined by $V_{i+1}$, $C_{i+1}$, $\langle\ ,\ \rangle_{i+1}$ and $\psi_{i+1}$.
In fact, the quotient $J^{i+1} \to V_{i+1}^\sharp$ factors through a quotient $J^{i+1} \to H^{i+1}$ and an isomorphism 
$
j_{i+1} : H^{i+1} \to V_{i+1}^\sharp,
$
where $H^{i+1}$ is a Heisenberg $p$-group in the sense of \cite{yu:01a}*{}.
%\labitem{Q3}{Q3} 
%\item
Finally, Yu constructs 
$
f_{i+1} : C^i \to \Sp(V_{i+1}),
$
such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $C^i$ on $H^{i+1}$ in the sense of \cite{yu:01a}.
Taken together, this defines
%\end{enumerate}
\begin{enumerate}
\labitem{Y4}{Y4}  a group homomorphism $h_{i+1} : C^i \ltimes J^{i+1} \to  \Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ making the following diagram commute.
\[
\begin{tikzcd}
1 \arrow{r} & J^{i+1} \arrow{d} \arrow{r} & C^i \ltimes J^{i+1} \arrow{d}{h_{i+1}} \arrow{r}{p_i} & C^i \arrow{r} \arrow{d}{f_i} & 1\\ 
1 \arrow{r} & V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \arrow{r} & 1
\end{tikzcd}
\]
\end{enumerate}

We can now recall how Yu uses all this to construct representations $\rho^i$ of $C^i$, for $i=1, \ldots, d$ and thus the type $(C,\rho) = (C^d,\rho^d)$.
The representations $\rho^i$ are defined recursively. 
For the base case $i=0$, the representation $\rho^0$ is part of the datum; see \ref{Y1} above.
%The key to defining the representation $\rho^{i+1}$ from $\rho^i$ is \ref{Y3}, above.
Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $C^i \ltimes J^{i+1}$.
Write $\inf(\rho^i \otimes \varphi^i)$ for the representation of $C^i \ltimes J^{i+1}$ obtained by pulling back $\rho^i$ along $C^i \ltimes J^{i+1} \to C^i$. 
Consider the representation
\begin{equation}\label{eq:tensor}
\rho_{i+1} \ceq h_{i+1}^*(W_{i+1}) \otimes \inf(\rho^i \otimes \varphi^i)
\end{equation}
of $C^i \ltimes J^{i+1}$.
%By construction, the character of this representation satisfies
%\begin{equation}\label{eq:tilderho}
%\trace({\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(y)\ \trace(\rho^i)(p_i(y))\ \varphi^i(p_i(y))
%\end{equation}
%for $y \in C^i \ltimes J^{i+1}$.
By \cite{yu:01a}*{}, the representation $\rho_{i+1}$ of $C^i \ltimes J^{i+1}$ is trivial on $C^{i}\cap J^{i+1}$ so $\rho_{i+1}$ descends to $C^{i+1}$. 
This defines the representation $\rho^{i+1}$ of $C^{i+1}$. \todo{I didn't use $\varphi^d$, so this can't be quite right.}
This completes the recursive definition and this determines $\rho^d = \rho$, which is the representation of $C^d = C$ determining the Yu type $(C,\rho)$.
%The character of $\rho^d$ on $C^d = C = J^0 \cdots J^d$ satisfies
%\[
%\trace(\rho)(k_0 \cdots k_d) = \rho^0(k_0)  \varphi^0(k_0) \cdots \varphi^d(k_d),
%\]
%for $k_i\in J^i$.

@@

%\begin{enumerate}
%\labitem{M1}{M1}
By \cite{yu:03a}*{Prop 10.2} there is a sequence  
\[
\underline{G}^0 \to \underline{G}^1 \to \cdots \to \underline{G}^d = \underline{G}
\]
of morphisms of affine smooth group schemes of finite type over $\OK$ such that, on $\OK$-points it gives the sequence $C^0 \subseteq C^1 \subseteq \cdots \subseteq C^d= C$ above.
Indeed, this is the main result of \cite{yu:03a}.

%\labitem{M2}{M2}
As explained in \cite{yu:03a}*{\S 10.4}, there is morphism of affine smooth group schemes of finite type over $\OK$ 
\[
\underline{J}^i \to \underline{G},
\] 
for each $i=0,\ldots d$, such that $\underline{J}^i(\OK) = J^i$ as a subgroup of $C$ and such that the image of the $\OK$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $C^i$, for $i=0, \ldots , d$.
%\labitem{M3}{M3}
There is a natural action of $\underline{G}^i$ on $\underline{J}^{i+1}$ in the category of smooth affine group schemes over $\OK$ so that the group scheme
\[
\underline{G}^i \ltimes \underline{J}^{i+1}
\]
gives $(\underline{G}^i \ltimes \underline{J}^{i+1})(\OK) = C^i \ltimes J^{i+1}$
%\end{enumerate}

@@

Write $\underline{J}^{i+1}_\Fq$ for the special fibre $\underline{J}^{i+1}\times_S S_1$ of $\underline{J}^{i+1}$. 
The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $V^{i+1}_\Fq$, where $V^{i+1}_\Fq$, appears as a quotient $J^{i+1}_\Fq \to V^{i+1}_\Fq$ of algebraic groups. Then the quotient $J^{i+1} \to V_{i+1}$ is realized as the composition
\[
\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to V^{i+1}_\Fq(\Fq) = V_{i+1}.
\]
Likewise, the Heisenberg $p$-group $H^{i+1}$, appearing in \ref{ssec:review}, may be realized as a quotient of algebraic groups, and $J^{i+1}\to H^{i+1}$ as the composition 
\[
\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to H^{i+1}_{\Fq}(\Fq) = H^{i+1}.
\]
Finally, the group homomorphism $f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ may be made geometric in much the same way. 
Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_S S_1$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ is realized as the composition
\[
\underline{G}^{i}(\OK) \to \underline{G}^{i}(\Fq) = \underline{G}^{i}_\Fq(\Fq) \to  \underline{G}^{i,\reductive}_\Fq(\Fq) \to W^{i+1}_{\Fq}(\Fq) = \Sp(V_{i+1}).
\]

With all this, we may revisit the quotients appearing in Section~\ref{ssec:review}:
\[
\begin{tikzcd}
1 \arrow{r} & \underline{J}^{i+1}  \arrow{r} & \underline{G}^i \ltimes \underline{J}^{i+1} \arrow{r} & \underline{G}^i \arrow{r}  & 1\\
1 \arrow{r} & \underline{J}^{i+1}_\Fq \arrow{d} \arrow{u} \arrow{r} & \underline{G}_\Fq^i \ltimes \underline{J}_\Fq^{i+1} \arrow{d} \arrow{u} \arrow{r} & \underline{G}_\Fq^i \arrow{r} \arrow{d} \arrow{u} & 1\\ 
1 \arrow{r} & V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \arrow{r} & 1,
\end{tikzcd}
\]
where the last two rows are now understood as forming a diagram in the category of algebraic groups over $\Fq$. 
This realizes the Jacobi group $\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp$ as a quotient of the special fibre of the smooth group scheme $\underline{G}^i \ltimes \underline{J}^{i+1}$ over $\OK$.

We may now revisit the ingredients in the construction of the representation $\rho$ of $\underline{G}(\OK)$ along the lines indicated by Yu and recalled in Section~\ref{ssec:review}.
\begin{enumerate}
\labitem{M0}{M0}
The compact groups $C^i$ have been replaced by the smooth group schemes $\underline{G}^i$.
\labitem{M1}{M1}
The continuous representation $\rho^0$ of $C^0$ is a representation of $\underline{G}^0(\OK)$ obtained by inflation along $\underline{G}^0(\OK) \to \underline{G}^0(\Fq)$ from a representation $\rho_0$ of $\underline{G}^0(\Fq) = \underline{G}^0_\Fq(\Fq)$.
In fact, $\rho_0$ is itself obtained by pulling back a representation $\rho_0^\reductive$ along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
\labitem{M2}{M2} The quasicharacters $\varphi^i$ are quasicharacters of $\underline{G}^i(\OK)$, for $i=0, \ldots d$.
\labitem{M3}{M3}
Diagram \eqref{eq:semiprod} is now replaced by the following diagram of smooth group schemes over $\OK$.
\begin{equation}\label{eq:pimodel}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && \underline{G}^{i}\times_{\underline{G}} \underline{J}^{i+1}\arrow{d} && \\
1 \arrow{r} & \underline{J}^{i+1} \arrow{r} & \underline{G}^i \ltimes \underline{J}^{i+1} \arrow{d} \arrow{r} & \underline{G}^i \arrow{r} & 1\\
&& \underline{G}^{i+1} \arrow{d} && \\
&& 1 &&
\end{tikzcd}
\end{equation}
\labitem{M4}{M4}
The representation $h_{i+1}^*(W_{i+1})$ appearing in \ref{Y4} is now obtained by pulling back a representation along 
\[
(\underline{G}^i \ltimes \underline{J}^{i+1})(\OK) \to (\underline{G}^i \ltimes \underline{J}^{i+1})(\Fq).
\]
Let $w_{i+1}$ be that representation of $(\underline{G}^i \ltimes \underline{J}^{i+1})(\Fq) = (\underline{G}_\Fq^i \ltimes \underline{J}^{i+1}_\Fq)(\Fq)$. 
Then $w_{i+1}$ is itself obtained by pulling back the representation $W_{i+1}$ along the $\Fq$-points of the quotient
\[
\underline{G}_\Fq^i \ltimes \underline{J}^{i+1}_\Fq \to 
\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp.
\]
\end{enumerate}

@@

\begin{proof}
%Now we explain how to geometrize the characters of these ingredient representations, using the discussion from Section~\ref{ssec:models}.  
Recall that $G^i(\Fq) = \underline{G}^i(R) = C^i$, canonically.
By continuity of the quasicharacters $\varphi^i : G^i(\Fq) \to \CC^\times$, there is some $m \in \NN$ and a factorization
\[
\begin{tikzcd}
G^i(\Fq) \arrow{rr}{\varphi^i} \arrow{rd} && \EEx\\
& \underline{G}^i(\OK/\mathfrak{p}^{m+1}) \arrow{ru}[swap]{\varphi^i_m} 
\end{tikzcd}
\] 
for each $i=0, \ldots d$.
Set $G_m^i = \Gr_m^{R}(\underline{G}^i)$.
Then $G_m^i$ is a smooth group scheme over $\Fq$ and $G_m^i(\Fq) = \underline{G}^i(R/\mathfrak{p}^{m+1})$, canonically.
Using Proposition~\ref{prop:quasicharacters}, let $\cs{L}^i_m$ be a geometrization of the linear character $\varphi^i_m: G_m^i \to \CC^\times$; so
\[
\trFrob{\cs{L}^i_m} = \trace \varphi^i_m.
\]
%Recall that the full Greenberg transform $\Gr^{\OK}(\underline{G}^i)$ is a group scheme over $\Fq$ such that $\Gr^{\OK}(\underline{G}^i)(\Fq) = \underline{G}^i(\Fq)$, canonically, and comes equipped with a morphism $\Gr^{\OK}(\underline{G}^i) \to \Gr^{\OK}_m(\underline{G}^i)$.
%Let $\cs{L}^i$ be the  Weil sheaf on $\Gr^{\OK}(\underline{G}^i)$ obtained from $\cs{L}^i_m$ by pullback along $\Gr^{\OK}(\underline{G}^i) \to \Gr^{\OK}_{m}(\underline{G}^i)$. 
%Then $\cs{L}^i$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^i)$ from which the quasicharacter $\varphi^i$ may be recovered.

>>>>

For use below, we recall some basic facts about the Heisenberg-Weil representation and make a conjecture about the geometrization of these representations.
We refer the reader to \cite{berndt-schmidt:98a} for more details.

@@

As proved in \cite{kim:07a}, all supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}.
The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from Yu's data. 
Let us refer to the types arising in this manner as {\it Yu types}.
%In this section we show that every Yu type is geometrizable.
% in a sense which will be made clear below.
%

A Yu type is then a pair $(C,\rho)$, where $C$ is a compact group and $\rho$ is a representation of $C$, directly from the following information, derived from a Yu datum:
\begin{enumerate}
\labitem{Y0}{Y0} a sequence of compact groups $C^0 \subseteq C^1 \subseteq \cdots \subseteq C^d= C$;
\labitem{Y1}{Y1} a continuous representation $\rho^0$ of $C^0$;
\labitem{Y2}{Y2} a quasicharacter $\varphi^i : C^i \to \CC^\times$, for $i=0, \ldots d$.
\end{enumerate}
The representations $(\rho^0, \varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct representations $\rho^i$ of $C^i$, for $i=1, \ldots, d$ such that $\rho^d = \rho$.

Since we will need some facts about this construction, we review some further detail here.

First, Yu introduces 
\begin{enumerate}
\labitem{Y3}{Y3}
compact groups $J^i\subset C$, for $i=0, \ldots d$, such that 
$
C^i = J^0\cdots J^{i}
$ 
and, for $i=0, \ldots d-1$, a natural action of $C^i$ on $J^{i+1}$ defining the groups $C^i \ltimes J^{i+1}$.
\begin{equation}\label{eq:semiprod}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && C^{i}\cap J^{i+1}\arrow{d} && \\
1 \arrow{r} & J^{i+1} \arrow{r} & C^i \ltimes J^{i+1} \arrow{d}{\pi_{i+1}} \arrow{r}{p_i} & C^i \arrow{r} & 1\\
&& C^{i+1} \arrow{d}{} && \\
&& 1 &&
\end{tikzcd}
\end{equation}
\end{enumerate}
%He then introduces the following quotients of $J^{i+1}$ and $C^i$, for $i=0, \ldots d-1$.

Next, Yu uses this to define a group homomorphism (in fact, a quotient) 
$
J^{i+1} \to V_{i+1}
$
where $V_{i+1}$ is a finite abelian group, the latter also given the structure of a $\Fq$-vector space.
The vector space $V_{i+1}$ is then equipped with a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$, where $C_{i+1}$ is a one-dimensional vector space over $\Fq$, itself equipped with an additive character $\psi_{i+1} : C_{i+1} \to \EEx$.
%\labitem{Q2}{Q2} 
%\item 
This, in turn, is used to define a map
$
J^{i+1} \to V_{i+1}^\sharp,
$
where $V_{i+1}^\sharp$ is the Heisenberg group determined by $V_{i+1}$, $C_{i+1}$, $\langle\ ,\ \rangle_{i+1}$ and $\psi_{i+1}$.
In fact, the quotient $J^{i+1} \to V_{i+1}^\sharp$ factors through a quotient $J^{i+1} \to H^{i+1}$ and an isomorphism 
$
j_{i+1} : H^{i+1} \to V_{i+1}^\sharp,
$
where $H^{i+1}$ is a Heisenberg $p$-group in the sense of \cite{yu:01a}*{}.
%\labitem{Q3}{Q3} 
%\item
Finally, Yu constructs 
$
f_{i+1} : C^i \to \Sp(V_{i+1}),
$
such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $C^i$ on $H^{i+1}$ in the sense of \cite{yu:01a}.

Taken together, this defines
%\end{enumerate}
\begin{enumerate}
\labitem{Y4}{Y4}  a group homomorphism $h_{i+1} : C^i \ltimes J^{i+1} \to  \Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ making the following diagram commute.
\[
\begin{tikzcd}
1 \arrow{r} & J^{i+1} \arrow{d} \arrow{r} & C^i \ltimes J^{i+1} \arrow{d}{h_{i+1}} \arrow{r}{p_i} & C^i \arrow{r} \arrow{d}{f_i} & 1\\ 
1 \arrow{r} & V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \arrow{r} & 1
\end{tikzcd}
\]
\end{enumerate}

We can now recall how Yu uses all this to construct representations $\rho^i$ of $C^i$, for $i=1, \ldots, d$ and thus the type $(C,\rho) = (C^d,\rho^d\otimes \varphi^d)$.
The representations $\rho^i$ are defined recursively. 
For the base case $i=0$, the representation $\rho^0$ is just $\rho_0$; see \ref{Y1} above.
Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $C^i \ltimes J^{i+1}$.
Write $\inf(\rho^i \otimes \varphi^i)$ for the representation of $C^i \ltimes J^{i+1}$ obtained by pulling back $\rho^i$ along $C^i \ltimes J^{i+1} \to C^i$. 
Consider the representation
\begin{equation}\label{eq:tensor}
\rho_{i+1} \ceq h_{i+1}^*(W_{i+1}) \otimes \inf(\rho^i \otimes \varphi^i)
\end{equation}
of $C^i \ltimes J^{i+1}$.
%By construction, the character of this representation satisfies
%\begin{equation}\label{eq:tilderho}
%\trace({\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(y)\ \trace(\rho^i)(p_i(y))\ \varphi^i(p_i(y))
%\end{equation}
%for $y \in C^i \ltimes J^{i+1}$.
By \cite{yu:01a}*{}, the representation $\rho_{i+1}$ of $C^i \ltimes J^{i+1}$ is trivial on $C^{i}\cap J^{i+1}$ so $\rho_{i+1}$ descends to $C^{i+1}$.

This defines the representation $\rho^{i+1}$ of $C^{i+1}$. 
This completes the recursive definition and thus determines $\rho^d$. 
Now set $\rho \ceq \rho^d\otimes \varphi^d$, which is the representation of $C^d = C$ determining the Yu type $(C,\rho)$.
%The character of $\rho^d$ on $C^d = C = J^0 \cdots J^d$ satisfies
%\[
%\trace(\rho)(k_0 \cdots k_d) = \rho^0(k_0)  \varphi^0(k_0) \cdots \varphi^d(k_d),
%\]
%for $k_i\in J^i$.

@@

%\begin{enumerate}
%\labitem{M1}{M1}
By \cite{yu:03a}*{Prop 10.2} there is a sequence  
\[
\underline{G}^0 \to \underline{G}^1 \to \cdots \to \underline{G}^d = \underline{G}
\]
of morphisms of affine smooth group schemes of finite type over $R$ such that, on $R$-points it gives the sequence $C^0 \subseteq C^1 \subseteq \cdots \subseteq C^d= C$ above.
Indeed, this is the main result of \cite{yu:03a}.

%\labitem{M2}{M2}
As explained in \cite{yu:03a}*{\S 10.4}, there is morphism of affine smooth group schemes of finite type over $R$ 
\[
\underline{J}^i \to \underline{G},
\] 
for each $i=0,\ldots d$, such that $\underline{J}^i(R) = J^i$ as a subgroup of $C$ and such that the image of the $R$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $C^i$, for $i=0, \ldots , d$.
%\labitem{M3}{M3}
There is a natural action of $\underline{G}^i$ on $\underline{J}^{i+1}$ in the category of smooth affine group schemes over $R$ so that the group scheme
\[
\underline{G}^i \ltimes \underline{J}^{i+1}
\]
gives $(\underline{G}^i \ltimes \underline{J}^{i+1})(R) = C^i \ltimes J^{i+1}$
%\end{enumerate}

@@

Write $\underline{J}^{i+1}_\Fq$ for the special fibre $\underline{J}^{i+1}\times_S S_1$ of $\underline{J}^{i+1}$. 
The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $V^{i+1}_\Fq$, where $V^{i+1}_\Fq$, appears as a quotient $J^{i+1}_\Fq \to V^{i+1}_\Fq$ of algebraic groups. Then the quotient $J^{i+1} \to V_{i+1}$ is realized as the composition
\[
\underline{J}^{i+1}(R) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to V^{i+1}_\Fq(\Fq) = V_{i+1}.
\]
Likewise, the Heisenberg $p$-group $H^{i+1}$, appearing in \ref{ssec:review}, may be realized as a quotient of algebraic groups, and $J^{i+1}\to H^{i+1}$ as the composition 
\[
\underline{J}^{i+1}(R) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to H^{i+1}_{\Fq}(\Fq) = H^{i+1}.
\]
Finally, the group homomorphism $f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ may be made geometric in much the same way. 
Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_S S_1$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ is realized as the composition
\[
\underline{G}^{i}(R) \to \underline{G}^{i}(\Fq) = \underline{G}^{i}_\Fq(\Fq) \to  \underline{G}^{i,\reductive}_\Fq(\Fq) \to W^{i+1}_{\Fq}(\Fq) = \Sp(V_{i+1}).
\]

With all this, we may revisit the quotients appearing in Section~\ref{ssec:review}:
\[
\begin{tikzcd}
1 \arrow{r} & \underline{J}^{i+1}  \arrow{r} & \underline{G}^i \ltimes \underline{J}^{i+1} \arrow{r} & \underline{G}^i \arrow{r}  & 1\\
1 \arrow{r} & \underline{J}^{i+1}_\Fq \arrow{d} \arrow{u} \arrow{r} & \underline{G}_\Fq^i \ltimes \underline{J}_\Fq^{i+1} \arrow{d} \arrow{u} \arrow{r} & \underline{G}_\Fq^i \arrow{r} \arrow{d} \arrow{u} & 1\\ 
1 \arrow{r} & V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \arrow{r} & 1,
\end{tikzcd}
\]
where the last two rows are now understood as forming a diagram in the category of algebraic groups over $\Fq$. 
This realizes the Jacobi group $\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp$ as a quotient of the special fibre of the smooth group scheme $\underline{G}^i \ltimes \underline{J}^{i+1}$ over $R$.

We may now revisit the ingredients in the construction of the representation $\rho$ of $\underline{G}(R)$ along the lines indicated by Yu and recalled in Section~\ref{ssec:review}.
\begin{enumerate}
\labitem{M0}{M0}
The compact groups $C^i$ have been replaced by the smooth group schemes $\underline{G}^i$.
\labitem{M1}{M1}
The continuous representation $\rho_0$ of $C^0$ is a representation of $\underline{G}^0(R)$ obtained by inflation along $\underline{G}^0(R) \to \underline{G}^0(\Fq)$ from a representation $\varrho_0$ of $\underline{G}^0(\Fq) = \underline{G}^0_\Fq(\Fq)$.
In fact, $\varrho_0$ is itself obtained by pulling back a representation $\varrho_0^\reductive$ along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
\labitem{M2}{M2} The quasicharacters $\varphi^i$ are quasicharacters of $\underline{G}^i(R)$, for $i=0, \ldots d$.
\labitem{M3}{M3}
Diagram \eqref{eq:semiprod} is now replaced by the following exact diagram of smooth group schemes over $R$.
\begin{equation}\label{eq:pimodel}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && \underline{G}^{i}\times_{\underline{G}} \underline{J}^{i+1}\arrow{d} && \\
1 \arrow{r} & \underline{J}^{i+1} \arrow{r} & \underline{G}^i \ltimes \underline{J}^{i+1} \arrow{d} \arrow{r} & \underline{G}^i \arrow{r} & 1\\
&& \underline{G}^{i+1} \arrow{d} && \\
&& 1 &&
\end{tikzcd}
\end{equation}
\labitem{M4}{M4}
The representation $h_{i+1}^*(W_{i+1})$ appearing in \ref{Y4} is now obtained by pulling back a representation along 
\[
(\underline{G}^i \ltimes \underline{J}^{i+1})(R) \to (\underline{G}^i \ltimes \underline{J}^{i+1})(\Fq).
\]
Let $w_{i+1}$ be that representation of $(\underline{G}^i \ltimes \underline{J}^{i+1})(\Fq) = (\underline{G}_\Fq^i \ltimes \underline{J}^{i+1}_\Fq)(\Fq)$. 
Then $w_{i+1}$ is itself obtained by pulling back the representation $W_{i+1}$ along the $\Fq$-points of the quotient
\[
\underline{G}_\Fq^i \ltimes \underline{J}^{i+1}_\Fq \to 
\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp.
\]
\end{enumerate}

@@

\begin{proof}
%Now we explain how to geometrize the characters of these ingredient representations, using the discussion from Section~\ref{ssec:models}.  
Recall that $G^i(\Fq) = \underline{G}^i(R) = C^i$, canonically.
By continuity of the quasicharacters $\varphi^i : G^i(\Fq) \to \CC^\times$, there is some $m \in \NN$ and a factorization
\[
\begin{tikzcd}
G^i(\Fq) \arrow{rr}{\varphi^i} \arrow{rd} && \EEx\\
& \underline{G}^i(R/\mathfrak{p}^{m+1}) \arrow{ru}[swap]{\varphi^i_m} 
\end{tikzcd}
\] 
for each $i=0, \ldots d$.
Set $G_m^i = \Gr_m^{R}(\underline{G}^i)$.
Then $G_m^i$ is a smooth group scheme over $\Fq$ and $G_m^i(\Fq) = \underline{G}^i(R/\mathfrak{p}^{m+1})$, canonically.
Using Proposition~\ref{prop:quasicharacters}, let $\cs{L}^i_m$ be a geometrization of the linear character $\varphi^i_m: G_m^i \to \CC^\times$; so
\[
\trFrob{\cs{L}^i_m} = \trace \varphi^i_m.
\]
%Recall that the full Greenberg transform $\Gr^{R}(\underline{G}^i)$ is a group scheme over $\Fq$ such that $\Gr^{R}(\underline{G}^i)(\Fq) = \underline{G}^i(\Fq)$, canonically, and comes equipped with a morphism $\Gr^{R}(\underline{G}^i) \to \Gr^{R}_m(\underline{G}^i)$.
%Let $\cs{L}^i$ be the  Weil sheaf on $\Gr^{R}(\underline{G}^i)$ obtained from $\cs{L}^i_m$ by pullback along $\Gr^{R}(\underline{G}^i) \to \Gr^{R}_{m}(\underline{G}^i)$. 
%Then $\cs{L}^i$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{R}(\underline{G}^i)$ from which the quasicharacter $\varphi^i$ may be recovered.

By \cite{lusztig:disconnected1}, there is a virtual Weil sheaf $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that ${\bar A}$ is a virtual character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
\[
\trFrob{A} = \trace \varrho_0^\reductive.
\]
(This uses the hypothesis that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.)
Let $A^0$ be the Weil sheaf on $(\underline{G}^0)_\Fq$ obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
Then 
\[
\trFrob{A^0} = \trace \varrho_0.
\]
The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg transform $G_0^0 = \Gr^{R}_0(\underline{G}^0)$ \cite{cunningham-roe:13a}*{\S 4.3}. 
With $m\in \NN$ as above, let ${A}_m^0$ be the Weil sheaf on the algebraic group $G_m^i$ obtained by pull-back from $A^0$ along the affine morphism $G_m^i \to G_0^0$.
Factor
\[
\begin{tikzcd}
G^0(\Fq) \arrow{rr}{\trace(\rho_0)} \arrow{rd} && \EE \\
& G_m^0(\Fq) \arrow{ru}[swap]{\trace(\rho_0)_m} 
\end{tikzcd}
\]
Observe that $\trace(\rho_0)_m$ may be recovered from ${A}_m^0$:
\[
\trFrob{{A}^0_m} = \trace(\rho_0)_m
\]
%Let $\cs{A}^0$ be the pull-back of $\cs{A}^0_m$ along  $\Gr^{R}(\underline{G}^0) \to \Gr^{R}_{m}(\underline{G}^0)$.
%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{R}(\underline{G}^0)$ from which the character of $\rho^0$ may be recovered.
